Radio Emission from Red-Giant Hot Jupiters

### 2015-09-28 ms.tex
caption for figure 4 is revised
caption for figure 5 is revised

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tbp]
   \plotonesc{cartoon_10Mj_100pc_smooth.pdf}
   \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_{\rm J}$ and the host red giants with 100 $R_{\odot }$.
The spectrum of RGHJ is modeled after Jovian radio spectra, e.g. figure 8 of \citet{zarka_et_al2004} and figure 2 of \citet{griesmeier2007a}; contribution from Io is not shown here.
The spectra of the host red giant are modeled simply by extrapolating observed radio spectra above 1~GHz with power law. }
  \label{fig:cartoon}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbhp]
   \plotoneh{radio_M-RG_1Mp.pdf}
   \plotoneh{radio_M-RG_10Mp.pdf}
   \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_{\rm J}$ (upper panel) and 10$M_{\rm J}$ (lower panel) at 1~AU (blue) and 5~AU (black).
Cross symbols indicate that the radio emission is not observable because cyclotron frequency is less than plasma density around the planet. }
  \label{fig:observability}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tbp]
   \plotonesc{cartoon_10Mj_100pc_smooth.pdf}
   \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_{\rm J}$ and the host red giants with 100 $R_{\odot }$.
The spectrum of RGHJ is modeled after Jovian radio spectra, e.g. Figure 8 of \citet{zarka_et_al2004} and Figure 2 of \citet{griesmeier2007a}; contribution from Io-DAM is not shown here.
The spectra of the host red giant are modeled simply by extrapolating observed radio spectra above 1~GHz with power law. }
  \label{fig:cartoon}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbhp]
   \plotoneh{radio_M-RG_1Mp.pdf}
   \plotoneh{radio_M-RG_10Mp.pdf}
   \caption{Radio flux from hypothetical RGHJs of 1$M_{\rm J}$ (upper panel) and 10$M_{\rm J}$ (lower panel) at 1~AU (blue) and 5~AU (black).
Cross symbols indicate that the radio emission is not observable because cyclotron frequency is less than plasma density around the planet. }
  \label{fig:observability}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
